---
title: "Project Campfire 2025 Quant Analysis"
author: "Garrett Jenkins"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
library(janitor)
```

```{r data_loading}

#CAMPFIRE_PRE <- read.csv("C:/Users/Garre/OneDrive/A Squared Analytics/Third Plateau/Campfire_Pre_Values.csv")

CAMPFIRE_PRE <- read.csv("C:/Users/Garre/OneDrive/A Squared Analytics/Third Plateau/Campfire_Pre_Labels.csv")

CAMPFIRE_POST <- read.csv("C:/Users/Garre/OneDrive/A Squared Analytics/Third Plateau/Endline.csv")

LABELS <- read.csv("C:/Users/Garre/OneDrive/A Squared Analytics/Third Plateau/Campfire_Pre_Labels.csv")

```

```{r pre_data_cleaning}

CAMPFIRE_PRE <- CAMPFIRE_PRE[-c(1:2),]

CAMPFIRE_PRE <- CAMPFIRE_PRE[order(CAMPFIRE_PRE$Name_2),]  ### Reviewed names visually and identified no duplicates

CAMPFIRE_PRE_CONSENT_FINISHED <- CAMPFIRE_PRE[-(which(CAMPFIRE_PRE$Consent != "Yes" | CAMPFIRE_PRE$Finished != "True")),]  ### Removed rows which did not have an affirmative consent value

CAMPFIRE_PRE_CONSENT_FINISHED[CAMPFIRE_PRE_CONSENT_FINISHED == ""] <- NA

CF_SUB_1 <- CAMPFIRE_PRE_CONSENT_FINISHED[which(CAMPFIRE_PRE_CONSENT_FINISHED$First.Time_10.12 != ""), ]

CF_SUB_2 <- CAMPFIRE_PRE_CONSENT_FINISHED[which(CAMPFIRE_PRE_CONSENT_FINISHED$First.Time.7.9 != ""), ]

CF_SUB_3 <- CAMPFIRE_PRE_CONSENT_FINISHED[which(CAMPFIRE_PRE_CONSENT_FINISHED$First.Time_3.6 != ""), ]

na_columns_1 <- names(CF_SUB_1)[colSums(is.na(CF_SUB_1)) == nrow(CF_SUB_1)]

na_columns_2 <- names(CF_SUB_2)[colSums(is.na(CF_SUB_2)) == nrow(CF_SUB_2)]

na_columns_3 <- names(CF_SUB_3)[colSums(is.na(CF_SUB_3)) == nrow(CF_SUB_3)]

CF_SUB_1 <- CF_SUB_1[,-which(names(CF_SUB_1) %in% na_columns_1)]

CF_SUB_2 <- CF_SUB_2[,-which(names(CF_SUB_2) %in% na_columns_2)]

CF_SUB_3 <- CF_SUB_3[,-which(names(CF_SUB_3) %in% na_columns_3)]

SUB_1_NAMES <- names(CF_SUB_1)

SUB_2_NAMES <- names(CF_SUB_2)

SUB_3_NAMES <- names(CF_SUB_3)

NAME_COMPS <- as.data.frame(cbind(SUB_1_NAMES, SUB_2_NAMES, SUB_3_NAMES))

NEW_COL_NAMES <- c(
                  'StartDate',
                  'EndDate',
                  'Status',
                  'IPAddress',
                  'Progress',
                  'Duration_Seconds',
                  'Finished',
                  'RecordedDate',
                  'ResponseId',
                  'LocationLatitude',
                  'LocationLongitude',
                  'DistributionChannel',
                  'UserLanguage',
                  'Q_RecaptchaScore',
                  'Q_RelevantIDDuplicate',
                  'Q_DuplicateRespondent',
                  'Q_RelevantIDDuplicateScore',
                  'Q_RelevantIDFraudScore',
                  'Q_RelevantIDLastStartDate',
                  'Consent',
                  'Name_1',
                  'Name_2',
                  'Gender',
                  'Attendance',
                  'First_Time',
                  'Summers',
                  'Activities',
                  'Activities_Text',
                  'Heritage',
                  'Belonging_Belonging',
                  'Belonging_Matter',
                  'Belonging_Included',
                  'Included',
                  'Joyful_Joyful',
                  'Joyful_Welcoming',
                  'Happy',
                  'Friendship',
                  'Connected',
                  'Post_Camp',
                  'Pathway',
                  'Giveaway_Name',
                  'Giveaway_Type',
                  'Donation_Memory',
                  'Donation_Memory_Text'
                )

names(CF_SUB_1) <- NEW_COL_NAMES

names(CF_SUB_2) <- NEW_COL_NAMES

names(CF_SUB_3) <- NEW_COL_NAMES

CAMPFIRE_PRE_CLEANED <- rbind(CF_SUB_1, CF_SUB_2, CF_SUB_3)

COLS_TO_DROP <- c("StartDate", "EndDate", "Status", "IPAddress", "Progress", "Duration_Seconds", "Finished", "RecordedDate",
                  "ResponseId", "LocationLatitude", "LocationLongitude", "DistributionChannel", "UserLanguage",
                  "Q_RecaptchaScore", "Q_RelevantIDDuplicate", "Q_DuplicateRespondent", "Q_RelevantIDDuplicateScore",
                  "Q_RelevantIDFraudScore", "Q_RelevantIDLastStartDate", "Consent", "Giveaway_Name",
                  "Donation_Memory_Text")

CAMPFIRE_PRE_CLEANED <- CAMPFIRE_PRE_CLEANED[,-which(names(CAMPFIRE_PRE_CLEANED) %in% COLS_TO_DROP)]

```

```{r post_data_cleaning}

CAMPFIRE_POST <- CAMPFIRE_POST[-c(1:2),]

CAMPFIRE_POST <- CAMPFIRE_POST[order(CAMPFIRE_POST$Name_2),]  ### Reviewed names visually and identified no duplicates

CAMPFIRE_POST_CONSENT_FINISHED <- CAMPFIRE_POST[-(which(CAMPFIRE_POST$Consent != "Yes" | CAMPFIRE_POST$Finished != "True")),]  ### Removed rows which did not have an affirmative consent value

CAMPFIRE_POST_CONSENT_FINISHED[CAMPFIRE_POST_CONSENT_FINISHED == ""] <- NA

CF_SUB_1 <- CAMPFIRE_POST_CONSENT_FINISHED[which(CAMPFIRE_POST_CONSENT_FINISHED$First.Time_10.12 != ""), ]

CF_SUB_2 <- CAMPFIRE_POST_CONSENT_FINISHED[which(CAMPFIRE_POST_CONSENT_FINISHED$First.Time.7.9 != ""), ]

CF_SUB_3 <- CAMPFIRE_POST_CONSENT_FINISHED[which(CAMPFIRE_POST_CONSENT_FINISHED$First.Time_3.6 != ""), ]

na_columns_1 <- names(CF_SUB_1)[colSums(is.na(CF_SUB_1)) == nrow(CF_SUB_1)]

na_columns_2 <- names(CF_SUB_2)[colSums(is.na(CF_SUB_2)) == nrow(CF_SUB_2)]

na_columns_3 <- names(CF_SUB_3)[colSums(is.na(CF_SUB_3)) == nrow(CF_SUB_3)]

CF_SUB_1 <- CF_SUB_1[,-which(names(CF_SUB_1) %in% na_columns_1)]

CF_SUB_2 <- CF_SUB_2[,-which(names(CF_SUB_2) %in% na_columns_2)]

CF_SUB_3 <- CF_SUB_3[,-which(names(CF_SUB_3) %in% na_columns_3)]

SUB_1_NAMES <- names(CF_SUB_1)

SUB_2_NAMES <- names(CF_SUB_2)

SUB_3_NAMES <- names(CF_SUB_3)

NAME_COMPS <- as.data.frame(cbind(SUB_1_NAMES, SUB_2_NAMES, SUB_3_NAMES))

CF_SUB_1 <- CF_SUB_1[,-(which(names(CF_SUB_1) %in% c("Q1", "Donation_Memory", "Donation_Memory_1_TEXT", "StartDate", "EndDate")))]

CF_SUB_2 <- CF_SUB_2[,-(which(names(CF_SUB_2) %in% c("Gender_5_TEXT", "StartDate", "EndDate")))]

CF_SUB_3 <- CF_SUB_3[,-(which(names(CF_SUB_3) %in% c("Donation_Memory", "StartDate", "EndDate")))]

NEW_COL_NAMES <- c(
                  'Status',
                  'IPAddress',
                  'Progress',
                  'Duration_Seconds',
                  'Finished',
                  'RecordedDate',
                  'ResponseId',
                  'LocationLatitude',
                  'LocationLongitude',
                  'DistributionChannel',
                  'UserLanguage',
                  'Q_RecaptchaScore',
                  'Q_RelevantIDDuplicate',
                  'Q_RelevantIDFraudScore',
                  'Consent',
                  'Name_1',
                  'Name_2',
                  'Gender',
                  'Attendance',
                  'First_Time',
                  'Summers',
                  'Activities',
                  'Activities_Text',
                  'Heritage',
                  'Belonging_Belonging',
                  'Belonging_Matter',
                  'Belonging_Included',
                  'Included',
                  'Return',
                  'Joyful_Joyful',
                  'Joyful_Welcoming',
                  'Happy',
                  'Friendship',
                  'Connected',
                  'Post_Camp',
                  'Pathway',
                  'Giveaway_Name',
                  'Giveaway_Type'
                )

names(CF_SUB_1) <- NEW_COL_NAMES

names(CF_SUB_2) <- NEW_COL_NAMES

names(CF_SUB_3) <- NEW_COL_NAMES

CAMPFIRE_POST_CLEANED <- rbind(CF_SUB_1, CF_SUB_2, CF_SUB_3)

COLS_TO_DROP <- c("StartDate", "EndDate", "Status", "IPAddress", "Progress", "Duration_Seconds", "Finished", "RecordedDate",
                  "ResponseId", "LocationLatitude", "LocationLongitude", "DistributionChannel", "UserLanguage",
                  "Q_RecaptchaScore", "Q_RelevantIDDuplicate", "Q_DuplicateRespondent", "Q_RelevantIDDuplicateScore",
                  "Q_RelevantIDFraudScore", "Q_RelevantIDLastStartDate", "Consent", "Giveaway_Name",
                  "Donation_Memory_Text")

CAMPFIRE_POST_CLEANED <- CAMPFIRE_POST_CLEANED[,-which(names(CAMPFIRE_POST_CLEANED) %in% COLS_TO_DROP)]

PRE_SUMMERS <- paste(Name_1, Name_2, sep = "")

POST_SUMMERS <- CAMPFIRE_POST_CLEANED[which(!paste(CAMPFIRE_POST_CLEANED$Name_1, CAMPFIRE_POST_CLEANED$Name_2, sep = "") %in% PRE_SUMMERS),]

POST_SUMMERS <- POST_SUMMERS[,-(which(names(POST_SUMMERS) %in% c("Return")))]

PRE_SUMMERS <- CAMPFIRE_PRE_CLEANED[-(which(names(CAMPFIRE_PRE_CLEANED) %in% c("Donation_Memory")))]

ALL_UNIQUE_CLEANED <- rbind(PRE_SUMMERS,POST_SUMMERS)

```

```{r data_analysis}

attach(CAMPFIRE_PRE_CLEANED)

```

<h1 align="center" id="heading"><b>Introduction Section</b></h1>

### Gender Counts and Percentages

#### Baseline

```{r gender_analysis_pre}

gender_counts <- table(Gender)

print(gender_counts) # Prints counts by gender

noquote(paste0(round(prop.table(gender_counts) * 100, 1),  '%')) # Prints % by gender

```

#### Endline

```{r gender_analysis_post}

gender_counts <- table(CAMPFIRE_POST_CLEANED$Gender)

print(gender_counts) # Prints counts by gender

noquote(paste0(round(prop.table(gender_counts) * 100, 1),  '%')) # Prints % by gender

```

### Grade Counts and Percentages

#### Baseline

```{r grade_analysis_pre}

grade_counts <- table(Attendance) 

print(grade_counts) # Prints counts by school grade

noquote(paste0(round(prop.table(grade_counts) * 100, 1), '%')) # Prints % by school grade

```

```{r grade_analysis_post}

grade_counts <- table(CAMPFIRE_POST_CLEANED$Attendance) 

print(grade_counts) # Prints counts by school grade

noquote(paste0(round(prop.table(grade_counts) * 100, 1), '%')) # Prints % by school grade

```

#### Endline

### Prior Camp Attendance Counts and Percentages

```{r attendance_analysis}












camp_before <- table(First_Time)

print(camp_before) # Prints counts by prior camp experience

noquote(paste0(round(prop.table(camp_before) * 100, 1), '%')) # Prints % by prior camp experience

```

#### Average # of Summers Previously Attended, for Those With Previous Experience

```{r attendance_analysis_avg_summers}

noquote(paste0(round(mean(as.numeric(substr(Summers,1,1)), na.rm = T), 1), " summers on average")) # For those who attended camp previously, returns the average number of summers

```
<h2 align="center" id="heading"><b>In the last year I...</b></h2>
### Attended Synagogue

```{r activities_analysis_synagoge}

Activities_List <- as.data.frame(table(unlist(strsplit(Activities, ",(?!\\s)", perl = TRUE))))

Attendance <- sum(Activities_List$Freq[grep("synagogue", Activities_List$Var1)])

Attendance_Perc = Attendance/47

print(Attendance)

noquote(paste0(round(Attendance_Perc * 100, 2), '%'))

```

### Participated in a Jewish Leadership Experience

```{r activities_analysis_leadership}

Activities_Cnt <- sum(Activities_List$Freq[grep("lead", Activities_List$Var1)])

Activities_Pct = Activities_Cnt/47

print(Activities_Cnt)

noquote(paste0(round(Activities_Pct * 100, 2), '%'))

```

### Celebrated Jewish Holidays

```{r activities_analysis_holidays}

Holiday_Cnt <- sum(Activities_List$Freq[grep("holidays", Activities_List$Var1)])

Holiday_Pct = Holiday_Cnt/47

print(Holiday_Cnt)

noquote(paste0(round(Holiday_Pct * 100, 2), '%'))

```

### Celebrated Shabbat

``` {r activities_analysis_shabbat}

Shabbat_Cnt <- sum(Activities_List$Freq[grep("Shabbat", Activities_List$Var1)])

Shabbat_Pct = Shabbat_Cnt/47

print(Shabbat_Cnt)

noquote(paste0(round(Shabbat_Pct * 100, 2), '%'))


```

### Volunteered With a Jewish Organization

``` {r activities_analysis_volunteer}

Volunteer_Cnt <- sum(Activities_List$Freq[grep("volunteer", Activities_List$Var1)])

Volunteer_Pct = Volunteer_Cnt/47

print(Volunteer_Cnt)

noquote(paste0(round(Volunteer_Pct * 100, 2), '%'))


```

### Participated in a Club

``` {r activities_analysis_club}

Club_Cnt <- sum(sum(Activities_List$Freq[grep("club", Activities_List$Var1)]),sum(Activities_List$Freq[grep("BBYO", Activities_List$Var1)]))

Club_Pct = Club_Cnt/47

print(Club_Cnt)

noquote(paste0(round(Club_Pct * 100, 2), '%'))

```

### Participated in Jewish Learning

``` {r activities_analysis_learning}

Learning_Cnt <- sum(Activities_List$Freq[grep("Hebrew", Activities_List$Var1)])

Learning_Pct = Learning_Cnt/47

print(Learning_Cnt)

noquote(paste0(round(Learning_Pct * 100, 2), '%'))

```
### Read About Jewish or Israeli Topics

``` {r activities_analysis_Israeli}

Israeli_Cnt <- sum(Activities_List$Freq[grep("Israeli", Activities_List$Var1)])

Israeli_Pct = Israeli_Cnt/47

print(Israeli_Cnt)

noquote(paste0(round(Israeli_Pct * 100, 2), '%'))

```

### No Jewish Activities Currently or in Last Year

``` {r activities_analysis_no_participation}

Activity_Cnt <- sum(sum(Activities_List$Freq[grep("I haven't", Activities_List$Var1)]),sum(Activities_List$Freq[grep("I am not", Activities_List$Var1)]))

Activity_Pct = Activity_Cnt/47

print(Activity_Cnt)

noquote(paste0(round(Activity_Pct * 100, 2), '%'))

```
### Did Something Else

``` {r activities_analysis_other}

Other_Cnt <- sum(sum(Activities_List$Freq[grep("Something else", Activities_List$Var1)]),sum(Activities_List$Freq[grep("Other", Activities_List$Var1)]))

Other_Pct = Other_Cnt/47

print(Other_Cnt)

noquote(paste0(round(Other_Pct * 100, 2), '%'))

```

<h1 align="center" id="heading"><b>Outcome One</b></h1>

<h3 align = "center" id="heading"><b>Participants form lasting connections with Jewish peers and feel a sense of belonging within a Jewish community</b></h3>

### How much do you agree with this statement: “I expect to feel like I belong at camp.”

``` {r Outcome_1_belong}

# Recoding the language used for the grades 3 - 6 survey to be consistent with the language used for grades 4 - 12 for reporting purposes. A note should be made of this in the report

Belonging_Belonging <- ifelse(Belonging_Belonging == 'Yes, a lot', 'Strongly agree',
                              ifelse(Belonging_Belonging == 'Yes, a little', 'Agree',
                                     ifelse(Belonging_Belonging == 'Kind of', 'Neither agree nor disagree',
                                            ifelse(Belonging_Belonging == 'Not really', 'Disagree',
                                                   ifelse(Belonging_Belonging == 'No, not at all', 'Strongly disagree',
                                                          Belonging_Belonging)))))

Outcome1_Belonging <- tabyl(Belonging_Belonging)

Outcome1_Belonging %>%
  adorn_totals("row") %>%
    adorn_pct_formatting()

```

### How much do you agree with this statement: “I expect to feel like I matter at camp.”

``` {r Outcome_1_matter}

# Recoding the language used for the grades 3 - 6 survey to be consistent with the language used for grades 4 - 12 for reporting purposes. A note should be made of this in the report

Belonging_Included <- ifelse(Belonging_Included == 'Yes, a lot', 'Strongly agree',
                              ifelse(Belonging_Included == 'Yes, a little', 'Agree',
                                     ifelse(Belonging_Included == 'Kind of', 'Neither agree nor disagree',
                                            ifelse(Belonging_Included == 'Not really', 'Disagree',
                                                   ifelse(Belonging_Included == 'No, not at all', 'Strongly disagree',
                                                          Belonging_Included)))))

Outcome1_Belonging <- tabyl(Belonging_Included)

Outcome1_Belonging %>%
  adorn_totals("row") %>%
    adorn_pct_formatting()

```

### How much do you agree with this statement: “I expect to feel included at camp.”

``` {r Outcome_1_included}

# Recoding the language used for the grades 3 - 6 survey to be consistent with the language used for grades 4 - 12 for reporting purposes. A note should be made of this in the report

Belonging_Matter <- ifelse(Belonging_Matter == 'Yes, a lot', 'Strongly agree',
                              ifelse(Belonging_Matter == 'Yes, a little', 'Agree',
                                     ifelse(Belonging_Matter == 'Kind of', 'Neither agree nor disagree',
                                            ifelse(Belonging_Matter == 'Not really', 'Disagree',
                                                   ifelse(Belonging_Matter == 'No, not at all', 'Strongly disagree',
                                                          Belonging_Matter)))))

Outcome1_Belonging <- tabyl(Belonging_Matter)

Outcome1_Belonging %>%
  adorn_totals("row") %>%
    adorn_pct_formatting()

```

### What are you most excited about when it comes to being a part of the Camp Seneca Lake community?

``` {r Outcome_1_excited_about}

print(Included)

```

<h1 align="center" id="heading"><b>Outcome Two</b></h1>

<h3 align = "center" id="heading"><b>Participants experience camp as a joyful, welcoming environment</b></h3>

### How much do you agree with this statement: “I expect camp to feel joyful.”

``` {r Outcome_2_joyful}

# Recoding the language used for the grades 3 - 6 survey to be consistent with the language used for grades 4 - 12 for reporting purposes. A note should be made of this in the report

Joyful_Joyful <- ifelse(Joyful_Joyful == 'Yes, a lot', 'Strongly agree',
                              ifelse(Joyful_Joyful == 'Yes, a little', 'Agree',
                                     ifelse(Joyful_Joyful == 'Kind of', 'Neither agree nor disagree',
                                            ifelse(Joyful_Joyful == 'Not really', 'Disagree',
                                                   ifelse(Joyful_Joyful == 'No, not at all', 'Strongly disagree',
                                                          Joyful_Joyful)))))

Outcome2_Joyful <- tabyl(Joyful_Joyful)

Outcome2_Joyful %>%
  adorn_totals("row") %>%
    adorn_pct_formatting()

```

### How much do you agree with this statement: “I expect camp to feel welcoming.”

``` {r Outcome_2_welcoming}

# Recoding the language used for the grades 3 - 6 survey to be consistent with the language used for grades 4 - 12 for reporting purposes. A note should be made of this in the report

Joyful_Welcoming <- ifelse(Joyful_Welcoming == 'Yes, a lot', 'Strongly agree',
                              ifelse(Joyful_Welcoming == 'Yes, a little', 'Agree',
                                     ifelse(Joyful_Welcoming == 'Kind of', 'Neither agree nor disagree',
                                            ifelse(Joyful_Welcoming == 'Not really', 'Disagree',
                                                   ifelse(Joyful_Welcoming == 'No, not at all', 'Strongly disagree',
                                                          Joyful_Welcoming)))))

Outcome2_Welcoming <- tabyl(Joyful_Welcoming)

Outcome2_Welcoming %>%
  adorn_totals("row") %>%
    adorn_pct_formatting()

```

### What do you think camp can do to help you feel happy or part of the group this summer?

``` {r Outcome_2_what}

print(Happy)

```

<h1 align="center" id="heading"><b>Outcome Three</b></h1>

<h3 align = "center" id="heading"><b>Participants develop meaningful relationships with their peers</b></h3>

### How much do you agree with this statement: “I expect to form meaningful friendships at camp this summer.”

```{r Outcome_3_friendships}

# Recoding the language used for the grades 3 - 6 survey to be consistent with the language used for grades 4 - 12 for reporting purposes. A note should be made of this in the report

Friendship <- ifelse(Friendship == 'Yes, a lot', 'Strongly agree',
                              ifelse(Friendship == 'Yes, a littlie', 'Agree',
                                     ifelse(Friendship == 'Kind of', 'Neither agree nor disagree',
                                            ifelse(Friendship == 'Not really', 'Disagree',
                                                   ifelse(Friendship == 'No, not at all', 'Strongly disagree',
                                                          Friendship)))))

Outcome3_Friendships <- tabyl(Friendship)

Outcome3_Friendships %>%
  adorn_totals("row") %>%
    adorn_pct_formatting()

```

### In what ways, if any, do you expect Camp Seneca Lake will help you to strengthen your relationships with other campers?

``` {r Outcome_3_connected}

print(Connected)

```

<h1 align="center" id="heading"><b>Outcome Four</b></h1>

<h3 align = "center" id="heading"><b>Families of participants become more integrated into Jewish life</b></h3>

<h3 align = "center" id="heading"><i>(Endline Survey Only)</i></h3>



<h1 align="center" id="heading"><b>Outcome Five</b></h1>

<h3 align = "center" id="heading"><b>Participants feel more connected to the Jewish community</b></h3>

### How much do you agree with this statement: “I expect that attending Camp Seneca Lake will strengthen my connection to the Jewish community.”

```{r Outcome_5_connection}

# Recoding the language used for the grades 3 - 6 survey to be consistent with the language used for grades 4 - 12 for reporting purposes. A note should be made of this in the report

Post_Camp <- ifelse(Post_Camp == 'Yes, a lot', 'Strongly agree',
                              ifelse(Post_Camp == 'Yes, a little', 'Agree',
                                     ifelse(Post_Camp == 'Kind of', 'Neither agree nor disagree',
                                            ifelse(Post_Camp == 'Not really', 'Disagree',
                                                   ifelse(Post_Camp == 'No, not at all', 'Strongly disagree',
                                                          Post_Camp)))))

Outcome5_Post_Camp <- tabyl(Post_Camp)

Outcome5_Post_Camp %>%
  adorn_totals("row") %>%
    adorn_pct_formatting()

```

```{r Outcome_5_pathways}

print(Pathway)

```

<h1 align="center" id="heading"><b>Incentive Choice</b></h1>

``` {r incentive_analysis}

Incentive_Choice <- tabyl(Giveaway_Type)

Incentive_Choice %>%
  adorn_totals("row") %>%
    adorn_pct_formatting()

```
